Hydrodynamics and rheology of an adhesive vesicle doublet

### 2019-02-09 vesicle_code/docs/adhesion/adhesion.tex
more changes by yny

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium configuration
  of a doublet of identical vesicles under adhesion in a quiescent flow.
  The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are
  labeled.  The color coding is the tension along the vesicle.  The
  vesicle length is fixed at $2\pi$, the dimensionless bending rigidity
  modulus is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and
  the separation distance is $\delta=0.2$.  {\em Left}: The overall
  equilibrium shapes of two vesicles under adhesive interactions vary
  with the reduced area.  {\em Right}: The membrane shapes in the
  contact region.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a $(m,n) = (12,6)$
L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
area decreases further, we observe undulation of the vesicle membrane on
the non-contact side while the contact region remains flat.  The color
coding along each curve is the tension of the vesicle membrane.  We
observe that the membrane tension in the contact region is very
negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

>>>>

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
%  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
   \includegraphics[keepaspectratio=true,scale=0.5]{figs/Dec18_vesicle_shape_vs_rA_composite.png}
  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configurations
  of a doublet of identical vesicles under adhesion in a quiescent flow at three values of $\Delta A$.
  The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are
  labeled.  The color coding is the tension along the vesicle.  The
  vesicle length is fixed at $2\pi$, the dimensionless bending rigidity
  modulus is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and
  the separation distance is $\delta=0.2$.  {\em Left}: The overall
  equilibrium shapes of two vesicles under adhesive interactions vary
  with the reduced area.  {\em Right}: The membrane shapes in the
  contact region.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a $(m,n) = (12,6)$
L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
area decreases further, we observe undulation of the vesicle membrane on
the non-contact side while the contact region remains flat.  The color
coding along each curve is the tension of the vesicle membrane.  We
observe that the membrane tension in the contact region is very
negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.
